\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-24 paper.tex
WIP design architecture

\newcommand{\uwds}{{\tt underworlds}\xspace}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{overview}
    \caption{Schema of a \uwds network: eight possible, user-written
    \emph{clients} (in blue) are exchanging environment models through four shared
    \emph{worlds} (made of joint spatial and temporal models). This architecture
    enables successive and modular refinement of the models
    (\emph{cascading} situation assessment), effectively adapted to each
    client's needs (yellow nodes represent other possible components in the system that do not
    interact directly with the \uwds network).}

@@

Each world is technically independent from every others. Dependencies between
worlds arise from the clients' connections. For instance, filters effectively
create a dependency between worlds. A client like the \textit{Physics-based
position correction} client create a dependency between the world {\tt base} (which
represents here the result of raw sensor fusion) and the world {\tt corrected}
which would be a physically-consistent copy of {\tt base}.

As a result, a \uwds network can be seen as a dependency graph (where
cyclic dependencies are permissible), and we call the whole architecture a
\emph{cascading situation assessment} system.

@@

\subsubsection{Nodes}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-photo2}
    \caption{}
    \label{}
\end{figure}
\uwds has been used within the European L2TOR project to...

@@

\subsection*{Architecture}

...diagram with the various \uwds clients

@@

\subsection{Future work}

>>>>

\newcommand{\uwds}{{\sc underworlds}\xspace}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{overview}
    \caption{Schema of a possible \uwds network: eight possible, user-written
    \emph{clients} (in blue) are exchanging environment models through four shared
    \emph{worlds} (made of joint spatial and temporal models). This architecture
    enables successive and modular refinement of the models
    (\emph{cascading} situation assessment), effectively adapted to each
    client's needs (yellow nodes represent other possible components in the system that do not
    interact directly with the \uwds network).}

@@

Each world is technically independent from every others. Dependencies between
worlds arise from the clients' connections. For instance, filters effectively
create a dependency between worlds. A client like the \textit{Physics-based
position correction} client create a dependency between the world {\tt base} (which
represents here the result of raw sensor fusion) and the world {\tt corrected}
which would be a physically-consistent copy of {\tt base}.
As a result, a \uwds network can be seen as a dependency graph between worlds (where
cyclic dependencies are permissible).

This architecture enables what we call \emph{cascading situation assessment}:
a set of independent software components (the clients) builds and refines
successive models of the environment by a combination of
filtering/transformations steps and model branching.

@@

\emph{Worlds} contain both a geometric model and a temporal model. The geometric
model is represented as a scene graph. The scene graph has a unique root node,
to which a tree of other nodes is parented.

Nodes in the scene graph have four possible types: \textbf{objects} that represent
concrete physical objects (typically with one or several associated 3D meshes);
\textbf{entities} that represent abstract entities like reference frames or
groups of objects; \textbf{perspectives} that represent viewpoints onto the
scene (like cameras or human gaze); and \textbf{fields} that represent scalar or
vector fields (like the visibility of an object, the working space of robot,
etc. -- note that fields are not yet implemented in the current version of
\uwds, see section~\ref{futurework}).

Every node has a unique ID, a parent, a 3D transformation relative to the parent
and an optional name. \emph{Object} nodes optionally store as well pointers to their
associated meshes.

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-photo2}
    \caption{A user manipulating objects on RFID mat while an operator monitors the interaction via an {\tt uwds view} client}
    \label{fig|l2torexample}
\end{figure}
\uwds has been used within the European L2TOR project~\cite{L2TOR} to implement

@@

\subsection*{Architecture}
The scenario consists of a number of \uwds clients that communicate with each other in order to provide an updated virtual representation to the operator. As seen in Figure \ref{fig|l2torexample}, the user interacts with some     
\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-timeline}
    \caption{Schema of the \uwds architecture used in L2TOR project pilot study. }
    \label{fig|l2torarchitecture}
\end{figure}
...diagram with the various \uwds clients

@@

\subsection{Future work}
\label{futurework}
